---
title: "Introduction to NLP with tidytext"
output: html_notebook
---

# The tidy text format
```{r message=FALSE, warning=FALSE}
library(janeaustenr)
library(tidyverse)
library(stringr)
library(tidytext)
library(wordcloud)
library(igraph)
library(ggraph)
```

```{r}
original_books <- austen_books() %>%
        group_by(book) %>%
        mutate(linenumber = row_number(),
               chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",ignore_case = T)))) %>%
        ungroup()

# regex: regular expressions
# roman numerals are represented by a string consisting of characters I,V,X,L,C and M
```

```{r}
tidy_books <- original_books %>%
        unnest_tokens(word, text)
# in a tidy format: one-token-per-row
```

```{r}
data("stop_words")
tidy_books <- tidy_books %>%
        anti_join(stop_words)
```

```{r}
tidy_books %>%
        count(word, sort = T)
# find the most common words
```

```{r}
tidy_books %>%
        count(word, sort = T) %>%
        filter(n > 600) %>%
        mutate(reorder(word, n)) %>%
        ggplot(aes(word,n)) + 
        geom_col() + 
        xlab(NULL) + 
        coord_flip()
```

# Sentiment analysis 
```{r}
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")
```

```{r}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

```{r}
ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

```{r}
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```
# Relationships between words: n-grams and correlations
```{r}
austen_bigrams <- austen_books() %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

austen_bigrams
```

```{r}
bigrams_separated <- austen_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigram_counts
```

```{r}
bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united
```

```{r}
bigram_tf_idf <- bigrams_united %>%
  count(book, bigram) %>%
  bind_tf_idf(bigram, book, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf
```

```{r}
# filter for only relatively common combinations
bigram_graph <- bigram_counts %>%
  filter(n > 20) %>%
  graph_from_data_frame()

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```

### You can find more details here: [Text Mining with R](https://www.tidytextmining.com/)

# Web scraping in tidy approach 
## Scrape a website using API: Motor Vehicle Collisions - Crashes
* We can directly access API from [NYC Open Data Initiative](https://opendata.cityofnewyork.us/) without having a key in advance. We will use [Motor Vehicle Collisions - Crashes](https://data.cityofnewyork.us/Public-Safety/Motor-Vehicle-Collisions-Crashes/h9gi-nx95) dataset as an example.  
```{r}
library(jsonlite)
nyc_crashes <- fromJSON("https://data.cityofnewyork.us/resource/h9gi-nx95.json") %>%
        as_tibble()
nyc_crashes
```



## Scrape a single website 
```{r}
library(rvest)
polisci_url <- read_html("https://www.polisci.washington.edu/people")
polisci_text <- polisci_url %>%
        html_nodes("table") %>%
        html_table(header=T) 
polisci_email <- polisci_text[[1]]$`Email / Phone` 
gsub(("(edu).*"), "\\1", polisci_email)
```
