---
title: "Introduction-to-NLP-with-Quanteda"
output: html_notebook
---

```{r message=FALSE}
library(quanteda)
library(readtext)
library(ggplot2)
```

# Basic R commands 
## Data types 
```{r}
x <- 2
class(x) # numeric: either double or integer
typeof(x) # double 

x <- 2L
class(x) # integer 
typeof(x) # integer: place an L after the value will produce an integer 

z <- c(1, 2.3, 5)
typeof(z) # double
is.double(z) # true
```

## Vectors, matrices and data frames 
```{r}
vec_num <- c(1, 5, 6, 3)
vec_num

vec_num[1] # R index starts from 1 
vec_num[1:3]

vec_num2 <- vec_num * 2  #arithmetic
vec_num2

vec_num3 <- append(vec_num,1:5, after = 4) #add values in a specific location
vec_num3

vec_char <- c('apple', 'banana', 'mandarin', 'melon')
vec_char2 <- paste(c('red', 'yellow', 'orange', 'green'), vec_char) #concatenate
vec_char2

names(vec_num) <- vec_char  #assign names to numbers
vec_num

vec_gt5 <- vec_num >= 5  #is the value greater than 5
vec_gt5

vec_textmatch <- vec_char == 'apple'  #does the text match
vec_textmatch
```

```{r}
dat_fruit <- data.frame(name = vec_char, count = vec_num)  #combines two vectors above
dat_fruit
nrow(dat_fruit)
ncol(dat_fruit)

dat_fruit_sub <- subset(dat_fruit, count >= 5)  #select only those cases by value
dat_fruit_sub

dat_fruit_sub2 <- subset(dat_fruit, name == 'apple') #by name
dat_fruit_sub2
```



```{r}
mat <- matrix(c(1, 3, 6, 8, 3, 5, 2, 7), nrow = 4)
mat 

rownames(mat) <- c('bag1', 'bag2', 'bag3', 'bag4') 
mat

colnames(mat) <- c('yep', 'nope') 
mat

dim(mat)

mat['bag1',1]  #first entry in brackets is row range; second is column

rowSums(mat)
colSums(mat)
```

# Processing textual data
## When working with textual data strings, it is recommended to turn R’s automatic conversion of strings into factors off.
```{r}
# Global options
options(stringsAsFactors = FALSE)
getwd()
# setwd("your path")
```

```{r}
file_path <- "https://raw.githubusercontent.com/kbenoit/readtext/master/inst/extdata/csv/inaugCorpus.csv"
file_text <- readtext(file_path, text_field = "texts")
file_text
```

```{r message=F}
# COnstruct a corpus, which is an extension of R list objects 
corp <- corpus(file_text)
summary(corp)

# For a more meaningful identifier 
docid <- paste(file_text$Year, 
               file_text$FirstName, 
               file_text$President, sep = " ")
docnames(corp) <- docid
summary(corp)

texts(corp[1])
cat(texts(corp[1])) # cat() will help to produce correct line breaks
```

## Familarizing with text statistics
```{r message=FALSE, warning=FALSE}
# To analyze which word forms the content, we need to tokenize the texts, which means all the words in the texts need to be identified and separated. A word form is also called "type"; the occurence of a type in a text is a "token"
tokens <- tokens(corp,remove_numbers=TRUE,remove_punct=TRUE,remove_symbols=TRUE,remove_separators=TRUE)
tokens <- tokens_remove(tokens, pattern = stopwords("en"))

# Create document-term matrix (DTM)
dtm <- dfm(tokens)
dim(dtm) # 5 rows and 1826 columns, meaning 5 documents in the corpus and 1826 word forms/types of the vocabulary after removing some meaningless stuff

# Sum columns for word counts
freqs <- colSums(dtm)

# Get vocabulary vector
words <- colnames(dtm)

# Combine words and their frequencies in a data frame
wordlist <- data.frame(words, freqs)

# reorder the wordlist by decreasing frequency
word_indexes <- order(wordlist[, "freqs"], decreasing = TRUE)
wordlist <- wordlist[word_indexes, ]

head(wordlist)
textplot_wordcloud(dtm)
```


# Web crawling and scraping 
## Scrape a series of documents
* Download and parse the tag overview page to extract all links to articles of interest
* Download and scrape each individual article page

Check out [here](https://tm4ss.github.io/docs/Tutorial_2_Web_crawling.html#4_optional_exercises) for more details 
```{r}
url <- "https://www.theguardian.com/world/angela-merkel"
html_document <- read_html(url)

links <- html_document %>%
    html_nodes(xpath = "//div[contains(@class, 'fc-item__container')]/a") %>%
    html_attr(name = "href")
head(links, 3)

page_numbers <- 1:3
base_url <- "https://www.theguardian.com/world/angela-merkel?page="
paging_urls <- paste0(base_url, page_numbers)

# View first 3 urls
head(paging_urls, 3)
```

```{r}
scrape_guardian_article <- function(url) {
    html_document <- read_html(url)
      
    title_xpath <- "//h1[contains(@class, 'content__headline')]"
    title_text <- html_document %>%
        html_node(xpath = title_xpath) %>%
        html_text(trim = T)
      
    intro_xpath <- "//div[contains(@class, 'content__standfirst')]//p"
    intro_text <- html_document %>%
        html_node(xpath = intro_xpath) %>%
        html_text(trim = T)
      
    body_xpath <- "//div[contains(@class, 'content__article-body')]//p"
    body_text <- html_document %>%
        html_nodes(xpath = body_xpath) %>%
        html_text(trim = T) %>%
        paste0(collapse = "\n")
      
    date_xpath <- "//time"
    date_text <- html_document %>%
        html_node(xpath = date_xpath) %>%
        html_attr(name = "datetime") %>%
        as.Date()
      
    article <- data.frame(
        url = url,
        date = date_text,
        title = title_text,
        body = paste0(intro_text, "\n", body_text)
        )
    
    return(article)
}
```

```{r}
all_articles <- data.frame()
for (i in 1:length(all_links)) {
    cat("Downloading", i, "of", length(all_links), "URL:", all_links[i], "\n")
    article <- scrape_guardian_article(all_links[i])
# Append current article data.frame to the data.frame of all articles
    all_articles <- rbind(all_articles, article)
}
```

```{r}
# View first articles
head(all_articles, 3)

# Write articles to disk
write.csv2(all_articles, file = "data/guardian_merkel.csv")
```

**More resources on quanteda:**

[quanteda: Quantitative Analysis of Textual Data](https://quanteda.io/index.html)

[quanteda tutorials](https://tutorials.quanteda.io/)

